---
title: "p8105_hw1_TS3175"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r Question_1}
la_df = tibble(
  norm_samp=rnorm(8),
  norm_samp_pos=norm_samp>0,
  vec_char=c("T", "A", "N", "U", "S", "R", "E", "E"),
  vec_factor= factor(c("cat", "dog", "snake", "cat", "dog", "snake", "cat", "dog")),
)
  mean(pull(la_df, norm_samp))
  mean(pull(la_df,norm_samp_pos))
  mean(pull(la_df,vec_char))
  mean(pull(la_df,vec_factor))
```
## The mean of norm_samp and norm_samp_pos works but the mean of vec_char and vec_factor do not.

```{r Question_1_cont, results="hide"} 
  mean(as.numeric(pull(la_df,norm_samp_pos)))
  mean(as.numeric(pull(la_df,vec_char)))
  mean(as.numeric(pull(la_df,vec_factor)))
```
## The mean of norm_samp and factor vector works but the mean of the character vector. It doesn't work for character vector because it cannot be translated into numbers.

```{r}
  pull(la_df,norm_samp)*(as.numeric(pull(la_df,norm_samp_pos)))
  pull(la_df,norm_samp)*(as.factor(pull(la_df,norm_samp_pos)))
  pull(la_df,norm_samp)*(as.numeric(as.factor(pull(la_df,norm_samp_pos))))
```

##Question 2

```{r}
set.seed(1234)
  graph_df = tibble(
  x=rnorm(500),
  y=rnorm(500),
  log_vec=x+y>1
  )
num_var=as.numeric(pull(graph_df,log_vec))
fac_var=as.factor(pull(graph_df,log_vec))
```
The data set has `r nrow(graph_df)` rows and `r ncol(graph_df)` columns
The mean of the sample is `r mean(pull(graph_df,x))`
The median of the sample is `r median(pull(graph_df,x))`
The standard deviation of the sample is `r median(pull(graph_df,x))`
The proportion of cases for which is `r mean(pull(graph_df,log_vec))`

```{r scatterplot}
  ggplot(graph_df, aes(x=x, y=y, color=log_vec)) + geom_point()
## In the scatterplot above, true is red and it means that the value of the sum of x and y is greater than. The blue is false and it means that the value of the sume of x and y is less than 1.

  ggplot(graph_df, aes(x=x, y=y, color=num_var)) + geom_point()
## In the scatterplot above, the lighter blue represents that the value of the sum of x and y is greater than. The darker blue represents that the value of the sume of x and y is less than 1.
  
  ggplot(graph_df, aes(x=x, y=y, color =fac_var)) + geom_point()
## In the scatterplot above, the blue represents that the value of the sum of x and y is greater than. The red represents that the value of the sume of x and y is less than 1.
  
   ggplot(graph_df, aes(x=x, y=y, color=log_vec)) + geom_point()
   ggsave("scatterplot.pdf", height = 4, width = 6)
```
