---
title: "p8105_hw1_TS3175"
Name: Tanu Sreedharan
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Below:A data frame with a random sample size of 8 from a standard normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length of 8, and a factor vector of length 8, with 3 different factor "levels"

```{r Question_1}
la_df = tibble(
  norm_samp=rnorm(8),
  norm_samp_pos=norm_samp>0,
  vec_char=c("T", "A", "N", "U", "S", "R", "E", "E"),
  vec_factor= factor(c("cat", "dog", "snake", "cat", "dog", "snake", "cat", "dog")),
)
  mean(pull(la_df, norm_samp))
  mean(pull(la_df,norm_samp_pos))
  mean(pull(la_df,vec_char))
  mean(pull(la_df,vec_factor))
```
## The mean of norm_samp and norm_samp_pos works but the mean of vec_char and vec_factor do not.

```{r Question_1_cont, results="hide"} 
  mean(as.numeric(pull(la_df,norm_samp_pos)))
  mean(as.numeric(pull(la_df,vec_char)))
  mean(as.numeric(pull(la_df,vec_factor)))
```
## The mean of norm_samp and factor vector works but the mean of the character vector. It doesn't work for character vector because it cannot be translated into numbers.

```{r}
  pull(la_df,norm_samp)*(as.numeric(pull(la_df,norm_samp_pos)))
  pull(la_df,norm_samp)*(as.factor(pull(la_df,norm_samp_pos)))
  pull(la_df,norm_samp)*(as.numeric(as.factor(pull(la_df,norm_samp_pos))))
```

##Question 2
##Below is a dataframe in which x is a random sample of 500 from a normal distribution and y is a random sample of 500 from a normal distribution and a logical vector in which x+y>1. It also has the logical vector coerced as a numeric vector and then factor vector. The dataframe also includes the number of rows and the number of columns of the dataset, the mean median, and standard deviation of x, and the proportion of cases or which x+y>1 

```{r}
set.seed(1234)
  graph_df = tibble(
  x=rnorm(500),
  y=rnorm(500),
  log_vec=x+y>1
  )
num_var=as.numeric(pull(graph_df,log_vec))
fac_var=as.factor(pull(graph_df,log_vec))
```
The data set has `r nrow(graph_df)` rows and `r ncol(graph_df)` columns
The mean of the sample is `r mean(pull(graph_df,x))`
The median of the sample is `r median(pull(graph_df,x))`
The standard deviation of the sample is `r median(pull(graph_df,x))`
The proportion of cases for which is `r mean(pull(graph_df,log_vec))`

##Below 3 scatterplots with descriptions below.

```{r scatterplot}
  ggplot(graph_df, aes(x=x, y=y, color=log_vec)) + geom_point()
## In the scatterplot above, true is red and it means that the value of the sum of x and y is greater than. The blue is false and it means that the value of the sume of x and y is less than 1.

  ggplot(graph_df, aes(x=x, y=y, color=num_var)) + geom_point()
## In the scatterplot above, the lighter blue represents that the value of the sum of x and y is greater than. The darker blue represents that the value of the sume of x and y is less than 1.
  
  ggplot(graph_df, aes(x=x, y=y, color =fac_var)) + geom_point()
## In the scatterplot above, the blue represents that the value of the sum of x and y is greater than. The red represents that the value of the sume of x and y is less than 1.
  
   ggplot(graph_df, aes(x=x, y=y, color=log_vec)) + geom_point()
   ggsave("scatterplot.pdf", height = 4, width = 6)
```
